Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-02-08 constantRate/ConstCompFuzzExt.tex
hartley entropy

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.  For a set of indices $\mathcal{I}$,  $X_{\mathcal{I}}$ is the restriction of $X$ to the indices in $\mathcal{I}$.  The set $\mathcal{I}^c$ is the complement of $\mathcal{I}$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ \lnote{I decided, after all, that $H_0(W)$ is less ambiguous and probably more commonly used than $|\cdot |$} be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.

@@

\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$}

@@

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_i$.  By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.  More formally, our construction is secure as long as enough blocks are unpredictable after adaptive queries:

\begin{definition}
\label{def:block guessable}
Let $I_w = (I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(\cdot, \cdot)$ be an oracle that returns \[(I^1,\dots,I^\ell)[q(n)]_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $A$ with oracle access to $I$ making at most $q$ queries
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

@@

The main change in \consref{cons:sampling} is that the obfuscated values are concatenated symbols of $W$.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.  A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we only need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of $v_i$s.

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\ell$ be a source in which all blocks $W_i$  are mutually independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in\mathcal{I}$, $\Hoo(W_i ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-unguessable block distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-unguessable block distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $i$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
&=\Hoo(W_i) - |A_1, \dots, A_q|\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

@@

By \defref{def:block guessable} there exists a set of indices $\mathcal{I}$ such that all blocks within $\mathcal{I}$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $\mathcal{I}$ are fixed.  Then $C | C_{\mathcal{I}^c} \overset{d}=C'$.  By \clref{cl:many locations ent}, we have that $\Hav(C|C_{\mathcal{I}^c} )= |C| -\beta$ and thus $\Hav(C'| C_{\mathcal{I}^c}) = |C| -\beta$.
Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that
\[
| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
\]
Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

\begin{proof}
\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
\begin{lemma}
\label{lem:codewords in I close}
Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then,
\[
\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\ell \log |Z|})) \le ( \ell -\beta) 2^{-(\alpha+1)}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.  The only information about the correct value of $c_i^*$ is contained in the query responses.  When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.  We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.  Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.  Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.  Thus, it must occur with probability:
\begin{align}
2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
 &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
\end{align}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
\label{cl:ent bounded away from n}
$\alpha \le n-\log q$
\end{claim}
\begin{proof}
It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in any block is at most $n-\log q$.  Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
This completes the proof of \clref{cl:ent bounded away from n}.
\end{proof}
\noindent
Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
\begin{align*}
 \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
 \end{align*}
 When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.  If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).  By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$. Recall that $c^*, c'$ match on all indices outside of $\mathcal{I}$. Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.  This concludes the proof of \lemref{lem:codewords in I close}
\end{proof}
By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) < (\ell -\beta)2^{-(\alpha+1)}$.  This completes the proof of \lemref{lem:sim cannot distinguish}.
\end{proof}

@@

\section{Proof of \lemref{lem:sampling works}}
\label{sec:proof of sampling lemma}
\begin{proof}
Consider some fixed $i$.
Recall that there a set $\mathcal{I}$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in \mathcal{I}$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.  Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $\cal{I}$. Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap \mathcal{I}|$.

\begin{claim}
\label{cl:vi have entropy}
\[
\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
\]
\end{claim}
\begin{proof}
Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.  We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.  Then
\begin{align*}
\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
\end{align*}
Taking the negative logarithm of both sides we have that
\begin{align*}
\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
&\ge \sum_{j_k\in \mathcal{I}} \alpha = \alpha X
\end{align*}
This completes the proof of \clref{cl:vi have entropy}.
\end{proof}

>>>>

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote $X = X_1,..., X_\ell$ as the concatenation of $X_1$ to $X_\ell$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.

@@

\lnote{since our construction takes random codewords, can't we afford to take the probability also over a random choice of $c$?}\bnote{I think so, what would need to change?  I think we might also be able to deal with just random neighbors?}

@@

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_i$.  By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.  More formally, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols. This restriction on the distribution is captured in the following definition.

\begin{definition}
\label{def:block guessable}
Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I$ making at most $q$ queries
\[
\forall i\in J, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}
\lnote{stopped going through section 4 here}

@@

The main change in \consref{cons:sampling} is that the obfuscated values are concatenated symbols of $W$.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.  A crucial difference is that the use of a computational primitive~(obfuscation) allows us to sample multiple times, because we only need to argue each $v_i$ has only individual entropy, as opposed to the information-theoretic setting, where it would be necessary to argue about the joint entropy of the $v_i$'s.

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\ell$ be a source in which all blocks $W_i$  are mutually independent.  Let $\alpha$ be a parameter.  Let $J\subset \{1,..., \ell\}$ be a set of indices such that for all $i\in J$, $\Hoo(W_i ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \ell - |J|)$-unguessable block distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |J|)$-unguessable block distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $i\in J, \Hav(W_i |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $i$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic (we can hardwire the best coins as nonuniform advice). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_j$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_i | View(A^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_i| A_1, \dots, A_q)\\
&=\Hoo(W_i) - H_0(A_1, \dots, A_q)\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

@@

By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.  Then $C | C_{J^c} \overset{d}=C'$.  By \clref{cl:many locations ent}, we have that $\Hav(C|C_{J^c} )= |C| -\beta$ and thus $\Hav(C'| C_{J^c}) = |C| -\beta$.
Let $D$ a distinguisher of size be some distinguisher of size at most $s_{sec}$ such that
\[
| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
\]
Define the distribution $X$ as follows:
\[X_i =
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

\begin{proof}
\noindent It suffices to show that for any two codewords that agree on $J^c$, the statistical distance is at most $(\ell-\beta)2^{-(\alpha+1)}$.
\begin{lemma}
\label{lem:codewords in I close}
Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then,
\[
\Delta( S^{I_X(\cdot, \cdot)}(c^*, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(c', 1^{\ell \log |Z|})) \le ( \ell -\beta) 2^{-(\alpha+1)}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in J$, $\Hav(W_i | View(S))\geq \alpha$.  The only information about the correct value of $c_i^*$ is contained in the query responses.  When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.  We now show that for any value of $c^*$ all queries on $i \in J$ return $0$ with probability $1-2^{-\alpha+1}$.  Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.  Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.  Thus, it must occur with probability:
\begin{align}
2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
 &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
\end{align}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
\label{cl:ent bounded away from n}
$\alpha \le n-\log q$
\end{claim}
\begin{proof}
It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in any block is at most $n-\log q$.  Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
This completes the proof of \clref{cl:ent bounded away from n}.
\end{proof}
\noindent
Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
\begin{align*}
 \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
 \end{align*}
 When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.  If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).  By the union bound over the indices $i\in J$ the total probability of a $1$ in $J$ is at most $(\ell-\beta)2^{-\alpha+1}$. Recall that $c^*, c'$ match on all indices outside of $J$. Thus, for all $c^*, c'$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.  This concludes the proof of \lemref{lem:codewords in I close}.
\end{proof}
By averaging over all points in $C'$ we conclude that $\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) < (\ell -\beta)2^{-(\alpha+1)}$.  This completes the proof of \lemref{lem:sim cannot distinguish}.
\end{proof}

@@

\section{Proof of \lemref{lem:sampling works}}
\label{sec:proof of sampling lemma}
\begin{proof}
Consider some fixed $i$.
Recall that there a set $J$  of size $\gamma - \beta = \Theta(\gamma)$ such that each $w$ and  block $j\in J$, $\Hoo(W_j | W_1 = w_1,..., W_{j-1}=w_{j-1}, W_{j+1}=w_{j+1},..., W_\gamma = w_\gamma) \geq \alpha$.  Since this is a worst case guarantee, the entropy of $V_i$ can be deduced from the number of symbols in $V_i$ that come from $J$. Namely, Denote by $X= |\{j_{i, 1},..., j_{i, \eta}\}\cap J|$.

\begin{claim}
\label{cl:vi have entropy}
\[
\Hoo(V_i |\Lambda = \lambda ) \geq \alpha X.
\]
\end{claim}
\begin{proof}
Denote by $j_1,..., j_\eta$ the indices selected by the randomness $\lambda_i$.  We begin by noting that $\Hoo(V_i |\Lambda = \lambda ) = -\log \max_{v\in V_i} \Pr[ V_i =v | \Lambda =\lambda] = -\log \max_{w_{j_1}, ..., w_{j_\eta}} \Pr[W_{j_1} = w_{j_1} \wedge \dots \wedge W_{j_\eta} w_{j_\eta}] $.  Then
\begin{align*}
\max_{w_{j_1},..., w_{j_\eta}} \Pr[ W_{j_1}=w_{j_1} \wedge \dots \wedge W_{j_\eta} = w_{j_\eta}]
&= \max_{w_{j_1},..., w_{j_\eta}} \prod_{k=1}^\eta \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
&\le \prod_{k=1}^\eta \max_{w_{j_1},..., w_{j_\eta}} \Pr[W_{j_k} = w_{j_k} | W_{j_{k-1}} = w_{j_{k-1}} \wedge ... \wedge W_{j_1} = w_{j_1}]\\
&\le\prod_{k=1}^\eta \max_{w_1,..., w_\gamma} \Pr[W_{j_k} = w_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1} ]\\
\end{align*}
Taking the negative logarithm of both sides we have that
\begin{align*}
\Hoo(V_i | \Lambda = \lambda) &\ge \sum_{k=1}^\eta \min_{w_1,..., w_\gamma} \Hoo(W_{j_k} | W_1 = w_1 \wedge ... \wedge W_{{j_k}-1} = w_{{j_k}-1})\\
&\ge \sum_{j_k\in J} \alpha = \alpha X
\end{align*}
This completes the proof of \clref{cl:vi have entropy}.
\end{proof}
